Supplementary Appendix

### 2023-06-27 manuscript/supplement.qmd
started a supplementary document

---
title: "Supplementary Appendix"
subtitle: "The FAIRification of pharmacoepidemiological research: A practical introduction to reproducible analytical workflows using git and R"
code-fold: true
eval: false
echo: true
number-sections: true

format: 
  pdf:
    fig-cap-location: top
    crossref:
    fig-title: "**Supplementary Figure**"

@@

```{r setup}
#| label: setup
#| include: false
#| eval: true
library(magick)
library(cowplot)
library(here)
```

**Authors**: Janick Weberpals^1^, Shirley V. Wang^1^

**Author affiliation**: ^1^Division of Pharmacoepidemiologyand Pharmacoeconomics, Department of Medicine, Brigham and Women's Hospital, Harvard Medical School, Boston, MA

@@

```{r}
#| label: fig-GitHub-gui_1
#| fig-cap: "Starting a new repository through the GitHub GUI."
#| eval: false
#| echo: false
#| out-width: 60%

sfig_a <- ggdraw() + 
  draw_image(image_read(here("manuscript/figures", "Figure_1a_new_repo.png")), scale = 0.5)

sfig_a
```

```{r}
#| label: fig-GitHub-gui
#| fig-cap: ""
#| eval: false
#| echo: false
#| out-width: 60%

sfig_a <- ggdraw() + 
  draw_image(image_read(here("manuscript/figures", "Figure_1a_new_repo.png")), scale = 0.5)

sfig_b <- ggdraw() + 
  draw_image(image_read(here("manuscript/figures", "Figure_1b_repo_info.png")))

sfig_c <- ggdraw() + 
  draw_image(image_read(here("manuscript/figures", "Figure_1c_clone.png")))

sfig1 <- plot_grid(
  fig_a, fig_c, fig_b, 
  nrow = 2,
  ncol = 2
)

sfig1
```

>>>>

---
title: "Supplementary Appendix"
subtitle: "The FAIRification of pharmacoepidemiological research: A practical introduction to reproducible analytical workflows using git and R"
code-fold: true
echo: false
number-sections: true

format: 
  pdf:
    fig-cap-location: top
    fig-align: center
    crossref:
      fig-title: "**Supplementary Figure**"
    toc: true
    toc-depth: 2
    number-sections: false
    colorlinks: true

@@

```{r setup}
#| label: setup
#| include: false
#| eval: true
library(magick)
library(cowplot)
library(here)
library(knitr)
```

@@

```{r}
#| label: fig-GitHub-gui_a
#| fig-cap: "Starting a new repository through the GitHub GUI."
#| out-width: 115%

include_graphics(here("manuscript/figures", "SFigure_1a_new_repo.png"))
```

```{r}
#| label: fig-GitHub-gui_b
#| fig-cap: "Populating basic information about the new repository."
#| out-width: 110%

include_graphics(here("manuscript/figures", "SFigure_2_repo_info.png"))
```

```{r}
#| label: fig-GitHub-gui_c
#| fig-cap: "Clone a GitHub repository using the HTTPS link and the git clone command"
#| out-width: 115%

include_graphics(here("manuscript/figures", "SFigure_3_clone.png"))
```
